Gravitational Lens Modelling of Flux Ratio Anomalous System B1555+375

### 2015-03-17 papers/B1555_EdgeOn/B1555_letter.tex
update to Table 1 and Table 4

 \hline
   HST				&		WFPC2    &  F555W		&	2009/01/20	&	5200\\
   HST				&		WFPC2    &  F814W		&	2009/01/20&	5200\\
   HST				&		NICMOS/NIC2	&	F160W	&	2012/08/09 & 5376\\
   Keck2			&		NIRC2 AO	&   $K^\prime$	& 2012/05/16	&  1800\\
   \hline
\end{tabular}
%\end{minipage}
\end{table}

@@

%\end{minipage}
\medskip
Comparision between radio and model-predicted lensed image positions. Observation data quoted from Table 2 in \citet{Marlow}. Position offsets are in unit of arcsec.

@@

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Flux ratios of B1555+375 components.}
  \begin{tabular}{@{}ccccc}

\hline
Flux ratio	& \multicolumn{2}{c}{MERLIN} & Model\\
		&5 GHz & 15 GHz  &\\
\hline
A/B			&$1.8$ & $1.8$ & $1.7$  \\ 
A/C 		&$2.0$ 	&$2.4$ &$2.2$  \\
A/D			&$13.0$ &$ 12.9$ & $8.0$  \\

@@

%\end{minipage}
\medskip
Comparision between radio data and model-predicted flux ratios. Radio observation data quoted from Table 2 and Table 3 in \citet{Marlow}.

>>>>

 \hline
   HST				&		WFPC2    &  F555W		&	2000/10/09 	&	5200\\
   HST				&		WFPC2    &  F814W		&	2000/10/09 &	5200\\
   HST				&		NICMOS/NIC2	&	F160W	&	2003/11/02 & 5376\\
   Keck2			&		NIRC2 AO	&   $K^\prime$	& 2012/05/16	&  1800\\
   \hline
\end{tabular}
%\end{minipage}
\end{table}

@@

%\end{minipage}
\medskip
Comparision between radio and model-predicted lensed image positions. Observation data quoted from Table 2 in \citet{Marlow}. Position offsets are in unit of arcsec. Both SIE+expdisk and 2-SIE lens models predict the same lens image positions.

@@

\begin{table}
% \centering
% \begin{minipage}{140mm}
  \caption{Flux ratios of B1555+375 components.}
  \begin{tabular}{@{}ccccccc}

\hline
	& \multicolumn{2}{c}{MERLIN} & \multicolumn{3}{c}{Model}\\
		&5 GHz & 15 GHz  & 1-SIE & SIE+expdisk & 2-SIE\\
\hline
A/B			&$1.75$ & $1.78$ &$1.07$& $1.66$ & $1.75$ \\ 
A/C 		&$2.05$ 	&$2.37$ &$2.95$ & $1.33$ & $2.16$\\
A/D			&$13.08$ &$ 12.86$ &$2.00$& $5.83$ & $7.96$\\

@@

%\end{minipage}
\medskip
Comparision between radio data and model-predicted flux ratios. Radio observation data is quoted from Table 2 and Table 3 in \citet{Marlow}. 1-SIE model is quoted from Tabel 5 in \citet{Marlow}.
